Topological Equivariant Artist Model

### 2022-01-07 slides/main.tex
sheaves

\begin{frame}
    \frametitle<0|handout:1>{Functor: \vindexc: \mathcal{\gbasec} \rightarrow \mathcal{\dbasec}}
    \frametitle<0|handout:2>{Data}
    \frametitle<0|handout:3>{Pullback: data to region of the visualization} 
    \frametitle<0|handout:4>{Graphic}
    \frametitle<0|handout:5>{Pushforward: visualization to index of data}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \onslide*<7-8|handout:4>{\sheafc_{\gbasec, \gtotalc}} 
            \onslide*<7-8,10-|handout:5>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<7-8|handout:5>{\textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc}}  
            \\
            \onslide*<2-|handout:1->{\gbasec}
            \onslide*<3-|handout:1->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<7-8,10-|handout:4>{\arrow[u, "\sheaf_{\gbasec, \gtotalc}", maps to, color=sheaf]}
            \onslide*<6,8-9,11-|handout:3>{\arrow[d, dashed, maps to, color=sheaf]} \&  \& 
            \onslide*<1-|handout:1->{\dbasec}
            \onslide*<4-6,8-9,11-|handout:2-3>{\arrow[d, "\sheaf_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<7-8,10-|handout:5>{\arrow[u, dashed, maps to, color=sheaf]} \\
            \onslide*<5-6,8|handout:3>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}} 
            \onslide*<5-6,8-9,11-|handout:3>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}  \& \& 
            \onslide*<4-6,8|handout:2-3>{\sheafc_{\dbasec, \dtotalc}}
        \end{tikzcd}
    \end{equation*}
    \only<4|handout:2>{
        \begin{itemize}
            \item $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item $\sheafc_{\dbasec, \dtotalc}:\opensetc \mapsto \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}, \opensetc \subset \dbasec$
            \item $\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \ni \dsectionc: \opensetc \rightarrow \dfiberc\restriction_{\opensetc}$
            \item $\dsectionc(\dbasepointc) = \{f_0:v_0, \cdots,\}, \dbasepointc \in \opensetc$
        \end{itemize}
    }
    \only<6|handout:3>{
        \begin{itemize}
            \item $\vindexpullc\dfiberc \hookrightarrow \vindexpullc\dtotalc \xrightarrow{\pi} \gbasec$
            \item $\vindexpullc\sheafc_{\dbasec,\dtotalc}:\opensetgc \mapsto \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}}, \opensetgc \subset \gbasec$
            \item $\cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}} \ni \vindexpullc\dsectionc: \opensetgc \rightarrow \vindexpullc\dfiberc\restriction_{\opensetgc}$
            \item $\vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)$
        \end{itemize}
    }
    \only<7|handout:4>{
        \begin{itemize}
            \item $\gfiberc \hookrightarrow \gtotalc \xrightarrow{\pi} \gbasec$
            \item $\sheafc_{\gbasec, \gtotalc}:\opensetgc \mapsto \cgamma{\opensetgc}{\dtotalc\restriction_{\opensetgc}}, \opensetgc \subset \gbasec$
            \item $\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \ni \gsectionc: \opensetgc \rightarrow \gfiberc\restriction_{\opensetgc}$
            \item $\gsectionc(\gbasepointc) = \{d_0, \cdots,\}, \dbasepointc \in \opensetfc$
        \end{itemize}
    }

\begin{frame}{
    \only<1-3|handout:1-3>{Pullback \& Pushforward are Isomorphic}
    \only<4|handout:4>{$\vartistc:\sheafc_{(\dbasec, \dtotalc)}\rightarrow \sheafc_{(\gbasec, \gtotalc)}$}
    \only<5-|handout:5->{$\vartistc: \dsectionc \mapsto \gsectionc$}
    }
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1-4|handout:1-4>{\sheafc_{(\gbasec, \gtotalc)}(\gbasec)} 
          \onslide*<5-|handout:5->{\{\gsectionc:\gbasepointc \scarr \setc\}}
          \onslide*<1-3|handout:1-3>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \onslide*<4-|handout:4->{\arrow[rr, "\vindexpushc", color=artist]} 
          \& \& 
          \onslide*<1-4|handout:1-4>{(\textcolor{functor}{\vindexpush}\sheafc_{(\gbasec, \gtotalc)})(\dbase)}
          \onslide*<5-|handout:5>{\{\vindexpushc \gsectionc: \dbasepointc \scarr\setc\}}
          \\
          \& \& \\
          \onslide*<1-4|handout:1-4>{(\textcolor{functor}{\vindexpull}\sheafc_{(\dbasec, \dtotalc)})(\gbasec)}
          \onslide*<5-|handout:5>{\{ \vindexpullc\dsectionc:\gbasepointc\scarr \setc\}}
          \onslide*<1-3|handout:1-3>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}
          \onslide*<4-|handout:4->{\arrow[rr, "\vindexpullc", color=artist]}
          \onslide*<2-3|handout:2-3>{\arrow[uu, "\textcolor{homset}{hom_{\gbasec}}", color=homset]} 
          \onslide*<4-|handout:4->{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist]}
          \&  \& 
          \onslide*<1-4|handout:1-4>{\sheafc_{(\dbasec, \dtotalc)}(\dbase)} 
          \onslide*<5-|handout:5->{\{\dsectionc:\dbasepointc \scarr \setc\}}
          \onslide*<2-3|handout:2-3>{\arrow[uu, "\textcolor{homset}{hom_{\dbasec}}"', color=homset]}
          \onslide*<4-|handout:4->{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist]}
          \onslide*<3|handout:3>{\arrow[lluu, "\textcolor{homset}{hom_{\dbasec,\gbasec}}"' description, dashed, color=homset]}
          \onslide*<4-|handout:4->{\arrow[lluu, "\vartistc"' description, dashed, color=artist]}
        \end{tikzcd}
      \end{equation*}

    \onslide<3|handout:3>{
        \begin{equation*}
        \textcolor{homset}{hom}_{\gbasec}(\textcolor{functor}{\vindexpull}\sheafc_{(\dbasec, \dtotalc)}, \sheafc_{(\gbasec, \gtotalc)}) = 
    \textcolor{homset}{hom}_{\dbase}(\sheafc_{(\dbasec, \dtotalc)}, \textcolor{functor}{\vindexpush}\sheafc_{(\gbasec, \gtotalc)})
        \end{equation*}
    }
    \onslide<4|handout:4>{
        \begin{equation*}
            \vartistc_{\vindexpull} = \vartistc_{\vindexpush}
        \end{equation*}
    }
\end{frame}

\begin{frame}{}

@@

>>>>

    \frametitle<0|handout:1>{Functor: \vindexc: \mathcal{\gbasec} \rightarrow \mathcal{\dbasec}}
    \frametitle<0|handout:2>{Data}
    \frametitle<0|handout:3>{Pullback: data to region of the visualization} 
    \frametitle<0|handout:4>{Graphic}
    \frametitle<0|handout:5>{Pushforward: visualization to index of data}
            \onslide*<7-8|handout:4-5>{\sheafc_{\gbasec, \gtotalc}} 
            \onslide*<7-8,10-|handout:5>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<7-8|handout:5>{\textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc}}  
            \\
            \onslide*<2-|handout:1,3->{\gbasec}
            \onslide*<3-|handout:1,3,5>{\arrow[rr, "\vindex", color=functor]}
            \onslide*<7-8,10-|handout:4-5>{\arrow[u, "\sheaf_{\gbasec, \gtotalc}", maps to, color=sheaf]}
            \onslide*<6,8-9,11-|handout:3>{\arrow[d, dashed, maps to, color=sheaf]} \&  \& 
            \onslide*<1-|handout:1-3,5>{\dbasec}
            \onslide*<4-6,8-9,11-|handout:2-3>{\arrow[d, "\sheaf_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<7-8,10-|handout:5>{\arrow[u, dashed, maps to, color=sheaf]} \\
            \onslide*<5-6,8|handout:3>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}} 
            \onslide*<5-6,8-9,11-|handout:3>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}  \& \& 
            \onslide*<4-6,8|handout:2-3>{\sheafc_{\dbasec, \dtotalc}}
    \only<4|handout:2>{
        \begin{itemize}
            \item $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item $\sheafc_{\dbasec, \dtotalc}:\opensetc \mapsto \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}, \opensetc \subset \dbasec$
            \item $\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \ni \dsectionc: \opensetc \rightarrow \dfiberc\restriction_{\opensetc}$
            \item $\dsectionc(\dbasepointc) = \{f_0:v_0, \cdots,\}, \dbasepointc \in \opensetc$
        \end{itemize}
    \only<6|handout:3>{
        \begin{itemize}
            \item $\vindexpullc\dfiberc \hookrightarrow \vindexpullc\dtotalc \xrightarrow{\pi} \gbasec$
            \item $\vindexpullc\sheafc_{\dbasec,\dtotalc}:\opensetgc \mapsto \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}}, \opensetgc \subset \gbasec$
            \item $\cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}} \ni \vindexpullc\dsectionc: \opensetgc \rightarrow \vindexpullc\dfiberc\restriction_{\opensetgc}$
            \item $\vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)$
        \end{itemize}
    \only<7|handout:4>{
        \begin{itemize}
            \item $\gfiberc \hookrightarrow \gtotalc \xrightarrow{\pi} \gbasec$
            \item $\sheafc_{\gbasec, \gtotalc}:\opensetgc \mapsto \cgamma{\opensetgc}{\dtotalc\restriction_{\opensetgc}}, \opensetgc \subset \gbasec$
            \item $\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \ni \gsectionc: \opensetgc \rightarrow \gfiberc\restriction_{\opensetgc}$
            \item $\gsectionc(\gbasepointc) = \{d_0, \cdots\}, \gbasepointc \in \opensetgc$
        \end{itemize}
    \only<7|handout:5>{
        \begin{itemize}
            \item $\vindexpushc\gfiberc \hookrightarrow \vindexpushc\gtotalc \xrightarrow{\pi} \dbasec$
            \item $\vindexpushc\sheafc_{\gbasec, \gtotalc}:\opensetc \mapsto \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}}, \opensetc \subset \dbasec$
            \item $\cgamma{\opensetc}{\gtotalc\restriction_{\opensetc}} \ni \gsectionc: \opensetc \rightarrow \gfiberc\restriction_{\opensetc}$
            \item $\vindexpushc\gsectionc(\gbasepointc) = \gsectionc\restriction_{\vindexpre(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexpre(\dbasepointc)$ 
        \end{itemize}

\end{frame}
.

@@

\begin{frame}{
    \only<1-3|handout:1-3>{Natural Transforms Between Sheaves}
    \only<4|handout:4>{$\vartistc:\sheafc_{(\dbasec, \dtotalc)}\rightarrow \sheafc_{(\gbasec, \gtotalc)}$}
    \only<5-|handout:5->{$\vartistc: \dsectionc \mapsto \gsectionc$}
    }
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1-4|handout:1>{\sheafc_{(\gbasec, \gtotalc)}(\gbasec)} 
          \onslide*<1-3|handout:1>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \onslide*<4-|handout:2->{\arrow[rr, "\vindexpushc", color=artist]} 
          \& \& 
          \onslide*<1-4|handout:1>{(\textcolor{functor}{\vindexpush}\sheafc_{(\gbasec, \gtotalc)})(\dbase)}
          \\
          \& \& \\
          \onslide*<1-4|handout:1>{(\textcolor{functor}{\vindexpull}\sheafc_{(\dbasec, \dtotalc)})(\gbasec)}
          \onslide*<1-3|handout:1>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}
          \onslide*<4-|handout:2->{\arrow[rr, "\vindexpullc", color=artist]}
          \onslide*<2-3|handout:1>{\arrow[uu, "\textcolor{nattran}{Nat_{\gbasec}}", color=nattran]} 
          \onslide*<4-|handout:2->{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist]}
          \&  \& 
          \onslide*<1-4|handout:1->{\sheafc_{\dbasec, \dtotalc}} 
          \onslide*<2-3|handout:1>{\arrow[uu, "\textcolor{nattran}{Nat_{\dbasec}}"', color=nattran]}
          \onslide*<4-|handout:2->{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist]}
          \onslide*<3|handout:1>{\arrow[lluu, " "' description, dashed, color=nattran]}
          \onslide*<4-|handout:2->{\arrow[lluu, "\vartistc"' description, dashed, color=artist]}
        \end{tikzcd}
      \end{equation*}

    \onslide<3|handout:3>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\gbasec}(\textcolor{functor}{\vindexpull}\sheafc_{(\dbasec, \dtotalc)}, \sheafc_{(\gbasec, \gtotalc)}) = 
    \textcolor{nattran}{Nat}_{\dbase}(\sheafc_{(\dbasec, \dtotalc)}, \textcolor{functor}{\vindexpush}\sheafc_{(\gbasec, \gtotalc)})
        \end{equation*}
    }
    \onslide<4|handout:4>{
        \begin{equation*}
            \vartistc_{\vindexpull} = \vartistc_{\vindexpush}
        \end{equation*}
    }
\end{frame}
